Manuscript results: Forecasting influenza using ARIMA and ARIMAX

### 2025-05-05 manuscript_results.Rmd
update

# Heatmap plot with models ordered by WeekAhead == 1  
plot_m_heatmap <- ggplot(p_df, aes(x = factor(WeekAhead), y = Model, fill = m)) +
  geom_tile(aes(fill = ifelse(Significance == "Significant", m, NA)), color = "black") +  # Fill only significant ones
  geom_tile(data = p_df %>% filter(Significance == "Not Significant"), 
            aes(x = factor(WeekAhead), y = Model), fill = "gray80", color = "black") +  # Gray for non-significant
  geom_text(aes(label = paste0("m:", round(m, 2),", sd:", round(sd, 2))), 
            color = "black", size = 4) +  # Add text labels
  scale_fill_gradient(low = "red", high = "cyan", na.value = "gray80", 
                      name = "Percentage (%)", limits = c(-35, 35)) +  # Fixed color scale from -30 to 30
  labs(title = "Mean model improvement and standard deviation comparing each model' WIS with the baseline across 48 states",
       subtitle = "Gray boxes indicate models not significantly different from the baseline model based on Wilcoxon test with Holm's adjusted p-values",
       x = "Week Ahead",
       y = "") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ Model_Type, scales = "free_y")  # Separate NoLg and other models

@@

# Plot the difference using ggplot2
ggplot(summed_data_all, aes(x = Julian_date, y = (Difference)*100, color = Week)) +
  geom_point(size = 3) +
  geom_hline(yintercept = 0, color = "black", linetype = "dashed", size = 0.8) +
  theme_minimal() +
  labs(
    title = "Mean percentage of WIS differences across all states",
    subtitle =  "AUTO_AVG_LB compared to baseline",
    x = "",
    y = "Difference (%)"
  ) +
  scale_y_continuous(
    limits = c(-100, 100),  # adjust if necessary
    breaks = seq(-100, 100, by = 20)
  ) +
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %y"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_color_manual(
    values = c("Week 1" = "#ffcccc",
               "Week 2" = "#ff6666",
               "Week 3" = "#cc0000",
               "Week 4" = "#990000")
  )
```

>>>>

# Heatmap plot with models ordered by WeekAhead == 1  
plot_m_heatmap <- ggplot(p_df, aes(x = factor(WeekAhead), y = Model, fill = m)) +
  geom_tile(aes(fill = ifelse(Significance == "Significant", m, NA)), color = "black") +  # Fill only significant ones
  geom_tile(data = p_df %>% filter(Significance == "Not Significant"), 
            aes(x = factor(WeekAhead), y = Model), fill = "gray80", color = "black") +  # Gray for non-significant
  geom_text(aes(label = paste0("m:", round(m, 2),", sd:", round(sd, 2))), 
            color = "black", size = 4) +  # Add text labels
  scale_fill_gradient(low = "red", high = "cyan", na.value = "gray80", 
                      name = "Percentage (%)", limits = c(-35, 35)) +  # Fixed color scale from -30 to 30
  labs(title = "Figure X: Mean differences between models' WIS and the baseline across 48 states",
       subtitle = "Gray boxes indicate models that are not significantly different from the baseline (p>0.05)",
         caption = "m = mean difference, sd = standard deviation",
       x = "Week Ahead",
       y = "") + 
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
  plot.caption = element_text(size = 12),
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),) +
  facet_wrap(~ Model_Type, scales = "free_y")  # Separate NoLg and other models

@@

# Plot the difference using ggplot2
model_improv<-ggplot(summed_data_all, aes(x = Julian_date, y = (Difference)*100, color = Week)) +
  geom_point(size = 3) +
  geom_hline(yintercept = 0, color = "black", linetype = "dashed", size = 0.8) +
  theme_minimal() +
  labs(
    title = "Figure X: Mean percentage of WIS differences across all states",
    subtitle = "AUTO_AVG_LB compared to baseline",
    x = "",
    y = "Difference (%)"
  ) +
  scale_y_continuous(
    limits = c(-100, 100),
    breaks = seq(-100, 100, by = 20)
  ) +
  scale_x_date(
    date_breaks = "1 month",
    date_labels = "%b %y"
  ) +
  scale_color_manual(
    values = c("Week 1" = "#ffcccc",
               "Week 2" = "#ff6666",
               "Week 3" = "#cc0000",
               "Week 4" = "#990000")
  ) +
  theme(
    plot.title = element_text(size = 18, face = "bold"),
    plot.subtitle = element_text(size = 14),
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

model_improv

ggsave(model_improv, height = 4.5, width = 9,  filename="Fig6.jpg")  
```
